---
title: "Qiime_analy"
author: "Julia Pierce (24366429)"
date: "3/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("phyloseq")
library("magrittr")
```
# Abstract

# Introduction

# Methods

# Results

##Data cleaning
Data were loaded into R.

## How does microbial community structure change with depth and oxygen ceocentration?

#### Alpha-diversity
Alpha-diversity and richness were calculated for the total community in R.
```{r, include=TRUE}
load("qiime2_phyloseq.RData")
```
Samples were rarefied/normalized to 100,000 sequences per sample to facilitate comparisons between samples. A random seed was set to ensure reproducibility.
```{r, include=TRUE}
set.seed(4832)
m.norm = rarefy_even_depth(qiime2, sample.size=100000)
```
Rarefied counts were converted to relative abundance percentages.
```{r, include=TRUE}
m.perc = transform_sample_counts(m.norm, function(x) 100 * x/sum(x))
```

```{r, include=TRUE}
# Calculation
m.alpha = estimate_richness(m.norm, measures = c("Chao1", "Shannon"))
m.meta.alpha = full_join(rownames_to_column(m.alpha), rownames_to_column(data.frame(m.perc@sam_data)), by = "rowname")
m.meta.alpha
```
Example plots
```{r, include=TRUE}
m.meta.alpha %>% 
  
ggplot() +
  geom_point(aes(x=Depth_m, y=Shannon)) +
   geom_smooth(method='auto', aes(x=as.numeric(Depth_m), y=Shannon)) +
  labs(title="Example 1: Alpha-diversity across depth", y="Shannon's diversity index", x="Depth (m)")

m.meta.alpha %>% 

ggplot() +
  geom_point(aes(x=O2_uM, y=Shannon)) +
  labs(title="Example 2: Alpha-diversity across oxygen", y="Shannon's diversity index", x="Oxygen (uM)")

m.meta.alpha %>% 
  mutate(O2_group = ifelse(O2_uM == 0, "anoxic", "oxic")) %>% 

# Use this in a plot
ggplot() +
  geom_boxplot(aes(x=O2_group, y=Shannon)) +
  labs(title="Example 3: Alpha-diversity by oxic/anoxic", y="Shannon's diversity index", x="Oxygen")
```

#### Taxa presence and abundance
Example plots using `phyloseq` for domain data. You should explore other taxonomy levels.
```{r, include=TRUE}
m.perc %>% 
plot_bar(fill="Domain") + 
  geom_bar(aes(fill=Domain), stat="identity") +
  labs(title="Example 4: Domains across samples")

m.perc %>% 
plot_bar() + 
  geom_bar(aes(fill=Domain), stat="identity") +
  facet_wrap(~Phylum, scales="free_y")+
  labs(title="Example 5: Phyla across samples")

m.perc %>% 
plot_bar() + 
  geom_bar(aes(fill=Domain), stat="identity") +
  facet_wrap(~Genus, scales="free_y")+
  labs(title="Example 6: Genus across samples")

```
Examples outside of phyloseq
```{r, include=TRUE}
m.perc %>%
  tax_glom(taxrank = 'Domain') %>%
  psmelt() %>% 

ggplot() +
  geom_boxplot(aes(x=Domain, y=Abundance)) +
  coord_flip() +
  labs(title="Example 7: Domain boxplots")

m.perc %>%
  tax_glom(taxrank = 'Genus') %>%
  psmelt() %>% 

ggplot() +
  geom_boxplot(aes(x=Genus, y=Abundance)) +
  coord_flip() +
  labs(title="Example 8: Genus boxplots")
```

## Does your taxon of interest *significantly* differ in abundance with depth and/or oxygen concentration?

Using the `magrittr` package, we can pipe our `tidyverse` modified data into linear models and other statiscal tests.

**Depth**
Linear model
```{r, include=TRUE}
m.norm %>% 
  subset_taxa(Family == "D_4__Oceanospirillaceae") %>% #THINK DOESN'T WORK CUZ CONTAINS NA VALUES? SO TRY RPLC THOSE
  tax_glom(taxrank = 'Family') %>%
  psmelt() %>%

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Plot to go along with linear model above.
```{r, include=TRUE}
m.perc %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>% 
  psmelt() %>% 
  group_by(Sample) %>% 
  summarize(Abundance_sum=sum(Abundance), Depth_m=mean(Depth_m)) %>% 
  
ggplot() +
  geom_point(aes(x=Depth_m, y=Abundance_sum)) +
  geom_smooth(method='lm', aes(x=as.numeric(Depth_m), y=Abundance_sum)) +
  labs(title="Example 9: Abundance of Family Oceanospirillaceae across depth")
```

**Oxygen**
Linear model
```{r, include=TRUE}
m.norm %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>% 
  tax_glom(taxrank = 'Family') %>%
  psmelt() %>%

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Plot to go along with linear model above.
```{r, include=TRUE}
m.perc %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>% 
  psmelt() %>% 
  group_by(Sample) %>% 
  summarize(Abundance_sum=sum(Abundance), O2_uM=mean(O2_uM)) %>% 
  
ggplot() +
  geom_point(aes(x=O2_uM, y=Abundance_sum)) +
  geom_smooth(method='lm', aes(x=as.numeric(O2_uM), y=Abundance_sum)) +
  labs(title="Example 10: Abundance of Genus Magnetococcus across oxygen")
```

## Within your taxon, what is the richness (number of OTUs/ASVs)?
Across all samples, there are 28 OTUs (*i.e.* taxa) within Genus *Magnetococcus*.
```{r}
m.norm %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") #%>%
  #tax_glom() %>%
  #summary()
```
Counting OTUs within Genus *Oceanospirillaceae* within each sample...
```{r}
m.norm %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>%
  otu_table()
```

## Do the abundances of OTUs/ASVs within your taxon of interest change *significantly* with depth and/or oxygen concentration?

**Depth**
General linear model for each OTU  
Asv107
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv107") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv120
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv120") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv131
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv131") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv213
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv213") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv243
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv243") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv417
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv417") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv476
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv476") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv668
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv668") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv810
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv810") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1050
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1050") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1152
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1152") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1283
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1283") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1352
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1352") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1414
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1414") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1430
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1430") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1486
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1486") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1490
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1490") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1570
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1570") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1593
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1593") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1797
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1797") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv1977
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1977") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2036
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2036") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2097
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2097") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2125
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2125") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2215
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2215") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2281
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2281") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2297
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2297") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
Asv2341
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2341") %>% 

  lm(Abundance ~ Depth_m, .) %>% 
  summary()
```
**Repeat for all OTUs within domain and then correct for multiple comparisons.**

This is all made up p-values.
```{r}
p.adjust(c(0.501, 0.031, 0.005, 0.324), method="fdr")
```

Plots to go along with these tests.
```{r}
m.perc %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>% 
  psmelt() %>% 
  
ggplot() +
  geom_point(aes(x=Depth_m, y=Abundance)) +
  geom_smooth(method='lm', aes(x=Depth_m, y=Abundance)) +
  facet_wrap(~OTU, scales="free_y") +
  labs(title="Example 11: Abundance of OTUs within Family Oceanospirillaceae across depth")
```

```{r}
m.perc %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>%
  psmelt() %>% 
  
ggplot() +
  geom_point(aes(x=Sample, y=OTU, size=Abundance, color=OTU)) + 
  scale_size_continuous(range = c(0,5)) +
  labs(title="Example 12: Abundance of OTUs within Family Oceanospirillaceae across depth")
```
**Oxygen**

General linear model for each OTU  
Asv107
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv107") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv120
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv120") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv131
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv131") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv213
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv213") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv243
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv243") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv417
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv417") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv476
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv476") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv668
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv668") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv810
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv810") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1050
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1050") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1152
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1152") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1283
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1283") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1352
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1352") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1414
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1414") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1430
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1430") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1486
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1486") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1490
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1490") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1570
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1570") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1593
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1593") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1797
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1797") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv1977
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv1977") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2036
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2036") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2097
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2097") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2125
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2125") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2215
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2215") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2281
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2281") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2297
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2297") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```
Asv2341
```{r}
m.norm %>% 
  psmelt() %>% 
  filter(OTU=="Asv2341") %>% 

  lm(Abundance ~ O2_uM, .) %>% 
  summary()
```

**Repeat for all OTUs within domain and then correct for multiple comparisons.**

This is all made up p-values.
```{r}
p.adjust(c(0.501, 0.031, 0.005, 0.324), method="fdr")
```

Plots to go along with these tests.
```{r}
m.perc %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>% 
  psmelt() %>% 
  
ggplot() +
  geom_point(aes(x=O2_uM, y=Abundance)) +
  geom_smooth(method='lm', aes(x=O2_uM, y=Abundance)) +
  facet_wrap(~OTU, scales="free_y") +
  labs(title="Example 11: Abundance of OTUs within Family Oceanospirillaceae across oxygen")
```

```{r}
m.perc %>% 
  subset_taxa(Family=="D_4__Oceanospirillaceae") %>%
  psmelt() %>% 
  
ggplot() +
  geom_point(aes(x=O2_uM, y=OTU, size=Abundance, color=OTU)) + 
  scale_size_continuous(range = c(0,5)) +
  labs(title="Example 12: Abundance of OTUs within Family Oceanospirillaceae across oxygen")
```

## Are the answers to the above the same using mothur and QIIME2 processed data?

# Discussion

# References
